A tutorial of Bayesian beta regressions with brms in R

### 2024-12-19 manuscript/manuscript.tex
edit according to Paul's comments

The coefficients of a beta regression are estimated on the log-odds
scale, as in Bernoulli/binomial (aka logistic) regressions. From the
summary, we see that speech rate (number of syllables per second) has a
positive effect on voicing proportion: the 80\% CrI is between 0.01 and
0.15 log-odds {[}\(\beta\) = 0.8, SD = 0.06{]}. Log-odds can be
converted to odd ratios by exponentiating the value: 0.01-0.15 log odds
correspond to an odd ratio of 1.01 to 1.16, or as percentages, to an
increase of voicing of 1 to 16\% for every increase of one syllable per
second. Since this is an 80\% CrI, we can be 80\% confident that the
true effect of speech rate is between 1-16\% increase of voicing
proportion, conditional on the data and model. Note that transforming
measures this way is appropriate \emph{only} with quantile-based
measures (like CrIs) but not with moments like the mean and standard
deviation: to correctly get mean and SDs in the transformed scale, you
must first extract the posterior draws (see below), convert them and
then take moments such as mean and SD (for a more detailed explanation,
see XXX).

@@

Once we have the posterior difference, we can obtain CrIs of the
difference using \texttt{quantile2()} from the posterior package. Beware
that the values of the difference are in log-odds! We can convert these
into odd ratios with \texttt{exp()}.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{voi\_prop\_bm\_diff }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{reframe}\NormalTok{(}
    \CommentTok{\# 90\% CrI}
    \AttributeTok{q90 =} \FunctionTok{quantile2}\NormalTok{(c2p\_tk\_diff, }\AttributeTok{probs =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.05}\NormalTok{, }\FloatTok{0.95}\NormalTok{)),}
    \CommentTok{\# 80\% CrI}
    \AttributeTok{q80 =} \FunctionTok{quantile2}\NormalTok{(c2p\_tk\_diff, }\AttributeTok{probs =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.1}\NormalTok{, }\FloatTok{0.9}\NormalTok{)),}
    \CommentTok{\# 60\% CrI}
    \AttributeTok{q60 =} \FunctionTok{quantile2}\NormalTok{(c2p\_tk\_diff, }\AttributeTok{probs =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.2}\NormalTok{, }\FloatTok{0.8}\NormalTok{)),}
\NormalTok{  ) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# exponentiate to get odd ratios and round to 2 digits}
  \FunctionTok{mutate}\NormalTok{(}\FunctionTok{across}\NormalTok{(}\FunctionTok{everything}\NormalTok{(), }\SpecialCharTok{\textasciitilde{}}\FunctionTok{round}\NormalTok{(}\FunctionTok{exp}\NormalTok{(.x), }\DecValTok{2}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{nasal }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(}\StringTok{"data/carignan2021/nasal.csv"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Rows: 705 Columns: 6
-- Column specification --------------------------------------------------------
Delimiter: ","
chr (5): speaker, label, vowel, NC, voicing
dbl (1): nas_prop

i Use `spec()` to retrieve the full column specification for this data.
i Specify the column types or set `show_col_types = FALSE` to quiet this message.
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{nasal}
\end{Highlighting}
\end{Shaded}

@@

Now let's calculate the mean nasalisation proportion within each draw by
voicing, and plot the resulting posterior distributions.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{nas\_prop\_bm\_draws\_long\_voicing }\OtherTok{\textless{}{-}}\NormalTok{ nas\_prop\_bm\_draws\_long }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# grouping by .draw and voicing ensures that averaging applies only within draw and voicing}
  \FunctionTok{group\_by}\NormalTok{(.draw, voicing) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# calculate the mean value within draw/voicing}
  \FunctionTok{summarise}\NormalTok{(}
    \AttributeTok{value\_mean =} \FunctionTok{mean}\NormalTok{(value), }\AttributeTok{.groups =} \StringTok{"drop"}
\NormalTok{  )}

\NormalTok{nas\_prop\_bm\_draws\_long\_voicing }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\FunctionTok{plogis}\NormalTok{(value\_mean), voicing)) }\SpecialCharTok{+}
  \FunctionTok{stat\_halfeye}\NormalTok{(}\AttributeTok{.width =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.6}\NormalTok{, }\FloatTok{0.8}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/nas-prop-bm-draws-long-voicing-1.pdf}}

The plot suggests an overall greater nasalisation proportion in
voiceless NC sequences. Let's quantify how greater as we did in Case
Study 1.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{nas\_prop\_bm\_diff }\OtherTok{\textless{}{-}}\NormalTok{ nas\_prop\_bm\_draws\_long\_voicing }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# pivot data to create one column per voicing with the mean drawn values,}
  \CommentTok{\# with one draw per raw}
  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ voicing, }\AttributeTok{values\_from =}\NormalTok{ value\_mean) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}
    \CommentTok{\# calculate the difference of voiceless and voiced}
    \AttributeTok{voicing\_diff =}\NormalTok{ voicingvoiceless }\SpecialCharTok{{-}}\NormalTok{ voicingvoiced}
\NormalTok{  )}

\NormalTok{nas\_prop\_bm\_diff }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{reframe}\NormalTok{(}
    \CommentTok{\# 90\% CrI}
    \AttributeTok{q90 =} \FunctionTok{quantile2}\NormalTok{(}\FunctionTok{exp}\NormalTok{(voicing\_diff), }\AttributeTok{probs =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.05}\NormalTok{, }\FloatTok{0.95}\NormalTok{)),}
    \CommentTok{\# 80\% CrI}
    \AttributeTok{q80 =} \FunctionTok{quantile2}\NormalTok{(}\FunctionTok{exp}\NormalTok{(voicing\_diff), }\AttributeTok{probs =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.1}\NormalTok{, }\FloatTok{0.9}\NormalTok{)),}
    \CommentTok{\# 60\% CrI}
    \AttributeTok{q60 =} \FunctionTok{quantile2}\NormalTok{(}\FunctionTok{exp}\NormalTok{(voicing\_diff), }\AttributeTok{probs =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.2}\NormalTok{, }\FloatTok{0.8}\NormalTok{)),}
\NormalTok{  ) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\FunctionTok{across}\NormalTok{(}\FunctionTok{everything}\NormalTok{(), }\SpecialCharTok{\textasciitilde{}}\FunctionTok{round}\NormalTok{(.x, }\DecValTok{2}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

@@

Moving onto question 2: is there individual speaker variation?
{[}TAMMINGA XXX{]} For this, we will use the \texttt{spread\_draws()}
function from tidybayes {[}XXX{]} to extract the draws of the varying
terms (in brms these are the coefficients that start with \texttt{r\_}).
There is quite a few steps of processing to get from the raw draws to
the estimand we need: while we have commented the following code, we
encourage readers to test each line sequentialy and inspect the
intermediate output to fully understand the process.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(tidybayes)}
\end{Highlighting}
\end{Shaded}

Attaching package: 'tidybayes'
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{nas\_prop\_r }\OtherTok{\textless{}{-}}\NormalTok{ nas\_prop\_bm }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# extract draws from model, only \textasciigrave{}r\_speaker\textasciigrave{} varying terms}
  \FunctionTok{spread\_draws}\NormalTok{(r\_speaker[speaker,voicingvowel]) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# separate the column voicingvowel to two columns}
  \FunctionTok{separate}\NormalTok{(voicingvowel, }\FunctionTok{c}\NormalTok{(}\StringTok{"voicing"}\NormalTok{, }\StringTok{"vowel"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# join the draws with the \textasciigrave{}b\_\textasciigrave{} terms}
  \FunctionTok{left\_join}\NormalTok{(}\AttributeTok{y =}\NormalTok{ nas\_prop\_bm\_draws\_long) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# get the expected log{-}odd value of each speaker, in each draw}
  \CommentTok{\# this is the sum of the \textasciigrave{}value\textasciigrave{} from the b\_ terms and the value from the}
  \CommentTok{\# r\_speaker term.}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{r\_speaker\_value =}\NormalTok{ value }\SpecialCharTok{+}\NormalTok{ r\_speaker) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# group the data for summarise}
  \FunctionTok{group\_by}\NormalTok{(.draw, speaker, voicing) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# get mean expected log{-}odds by draw, speaker and voicing (averaging across vowel)}
  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{r\_speaker\_value\_mean =} \FunctionTok{mean}\NormalTok{(r\_speaker\_value)) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# make the data wider: two columns, one for voiced and one for voiceless}
  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ voicing, }\AttributeTok{values\_from =}\NormalTok{ r\_speaker\_value\_mean) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# finally, calculate the difference in expected log{-}odds of voiceless and voiced}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{voicing\_diff =}\NormalTok{ voicingvoiceless }\SpecialCharTok{{-}}\NormalTok{ voicingvoiced)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Joining with `by = join_by(voicing, vowel, .chain, .iteration, .draw)`
\end{verbatim}

\begin{verbatim}
`summarise()` has grouped output by '.draw', 'speaker'. You can override using
the `.groups` argument.
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{nas\_prop\_r}
\end{Highlighting}
\end{Shaded}

>>>>

The coefficients of a beta regression are estimated on the log-odds
scale, as in Bernoulli/binomial (aka logistic) regressions. From the
summary, we see that speech rate (number of syllables per second) has a
positive effect on voicing proportion: the 80\% CrI is between 0.01 and
0.15 log-odds {[}\(\beta\) = 0.8, SD = 0.06{]}. Log-odds can be
converted to odd-ratios by exponentiating the value: 0.01-0.15 log odds
correspond to an odd-ratio of 1.01 to 1.16, or as percentages, to an
increase of voicing of 1 to 16\% for every increase of one syllable per
second. Since this is an 80\% CrI, we can be 80\% confident that the
true effect of speech rate is between 1-16\% increase of voicing
proportion, conditional on the data and model. Note that transforming
measures this way is appropriate \emph{only} with quantile-based
measures (like CrIs) but not with moments like the mean and standard
deviation: to correctly get mean and SDs in the transformed scale, you
must first extract the posterior draws (see below), convert them and
then take moments such as mean and SD (for a more detailed explanation,
see XXX). In the avoidance of doubt, we will always transform the drawn
values first and then take summary measures.

@@

Once we have the posterior difference, we can obtain CrIs of the
difference using \texttt{quantile2()} from the posterior package. Beware
that the values of the difference are in log-odds! We can convert these
into odd-ratios with \texttt{exp()}. odd-ratios indicate the ratio of
the difference between A and B, so that 1 means no difference, values
greater than 1 indicate an increase in A relative to B and values lower
than 1 indicate a decrease in A relative to B. odd-ratios are useful
when looking at differences that are in log-odds because while the
relative magnitude of the difference in proportion between two groups is
the same independent of the baseline proportion, the \emph{absolute}
magnitude of the difference depends on the baseline value. For example,
an odd-ratio difference of 1.25 would correspond to a proportion
increase of 13 percentage points if the baseline proportion is 0.62 but
it would correspond to a proportion increase of 17 percentage points if
the baseline proportion is 0.73. Of course, in real research contexts it
is still usefull to think about absolute magnitudes and their relevance
from a conceptual and methodological perspective. In this tutorial we
just focus on odd-ratios for simplicity.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{voi\_prop\_bm\_diff }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{c2p\_tk\_diff\_ratio =} \FunctionTok{exp}\NormalTok{(c2p\_tk\_diff)) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{reframe}\NormalTok{(}
    \CommentTok{\# 90\% CrI}
    \AttributeTok{q90 =} \FunctionTok{quantile2}\NormalTok{(c2p\_tk\_diff\_ratio, }\AttributeTok{probs =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.05}\NormalTok{, }\FloatTok{0.95}\NormalTok{)),}
    \CommentTok{\# 80\% CrI}
    \AttributeTok{q80 =} \FunctionTok{quantile2}\NormalTok{(c2p\_tk\_diff\_ratio, }\AttributeTok{probs =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.1}\NormalTok{, }\FloatTok{0.9}\NormalTok{)),}
    \CommentTok{\# 60\% CrI}
    \AttributeTok{q60 =} \FunctionTok{quantile2}\NormalTok{(c2p\_tk\_diff\_ratio, }\AttributeTok{probs =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.2}\NormalTok{, }\FloatTok{0.8}\NormalTok{)),}
\NormalTok{  ) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# round to 2 digits}
  \FunctionTok{mutate}\NormalTok{(}\FunctionTok{across}\NormalTok{(}\FunctionTok{everything}\NormalTok{(), }\SpecialCharTok{\textasciitilde{}}\FunctionTok{round}\NormalTok{(.x, }\DecValTok{2}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{nasal }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(}\StringTok{"data/carignan2021/nasal.csv"}\NormalTok{)}
\NormalTok{nasal}
\end{Highlighting}
\end{Shaded}

@@

Now let's calculate the mean nasalisation proportion within each draw by
voicing, and plot the resulting posterior distributions. Note that, as
discussed for Case study 1, when working wit log-odds it is important to
first do all necessary calculations in log-odds, here calculate the mean
log-odds across vowels, and \emph{then} transform the calculated
estimands to proportions/probabilities.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{nas\_prop\_bm\_draws\_long\_voicing }\OtherTok{\textless{}{-}}\NormalTok{ nas\_prop\_bm\_draws\_long }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# grouping by .draw and voicing ensures that averaging applies only within draw and voicing}
  \FunctionTok{group\_by}\NormalTok{(.draw, voicing) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{summarise}\NormalTok{(}
    \CommentTok{\# calculate the mean value within draw/voicing in log{-}odds}
    \AttributeTok{value\_mean =} \FunctionTok{mean}\NormalTok{(value),}
    \CommentTok{\# we can now transform log{-}odds to proportion with plogis()}
    \AttributeTok{value\_mean\_prop =} \FunctionTok{plogis}\NormalTok{(value\_mean),}
    \AttributeTok{.groups =} \StringTok{"drop"}
\NormalTok{  )}

\NormalTok{nas\_prop\_bm\_draws\_long\_voicing}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# A tibble: 8,000 x 4
   .draw voicing          value_mean value_mean_prop
   <int> <chr>                 <dbl>           <dbl>
 1     1 voicingvoiced       -0.406            0.400
 2     1 voicingvoiceless    -0.0804           0.480
 3     2 voicingvoiced       -0.391            0.404
 4     2 voicingvoiceless    -0.123            0.469
 5     3 voicingvoiced       -0.444            0.391
 6     3 voicingvoiceless    -0.132            0.467
 7     4 voicingvoiced       -0.439            0.392
 8     4 voicingvoiceless    -0.0982           0.475
 9     5 voicingvoiced       -0.383            0.405
10     5 voicingvoiceless    -0.266            0.434
# i 7,990 more rows
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{nas\_prop\_bm\_draws\_long\_voicing }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(value\_mean\_prop, voicing)) }\SpecialCharTok{+}
  \FunctionTok{stat\_halfeye}\NormalTok{(}\AttributeTok{.width =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.6}\NormalTok{, }\FloatTok{0.8}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/nas-prop-bm-draws-long-voicing-plot-1.pdf}}

The plot suggests an overall greater nasalisation proportion in
voiceless NC sequences. Let's quantify how greater as we did in Case
Study 1. We will use odd-ratios in this context as well, i.e.~we will
convert log-odds to odd-ratios using the \texttt{exp()} (exponential)
function (and as before we first calculate the difference and then
exponentiate the resulting values, after which we can take summary
measures, like means and quantile-based measures such as CrIs).

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{nas\_prop\_bm\_diff }\OtherTok{\textless{}{-}}\NormalTok{ nas\_prop\_bm\_draws\_long\_voicing }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# pivot data to create one column per voicing with the mean drawn values,}
  \CommentTok{\# with one draw per raw. we need to drop the value\_mean\_prop col}
  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{value\_mean\_prop) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ voicing, }\AttributeTok{values\_from =}\NormalTok{ value\_mean) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}
    \CommentTok{\# calculate the difference of voiceless and voiced in log{-}odds}
    \AttributeTok{voicing\_diff =}\NormalTok{ voicingvoiceless }\SpecialCharTok{{-}}\NormalTok{ voicingvoiced,}
    \CommentTok{\# now transform with exp() to get the ratio difference}
    \AttributeTok{voicing\_diff\_ratio =} \FunctionTok{exp}\NormalTok{(voicing\_diff)}
\NormalTok{  )}
\NormalTok{nas\_prop\_bm\_diff}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# A tibble: 4,000 x 5
   .draw voicingvoiced voicingvoiceless voicing_diff voicing_diff_ratio
   <int>         <dbl>            <dbl>        <dbl>              <dbl>
 1     1        -0.406          -0.0804        0.325               1.38
 2     2        -0.391          -0.123         0.268               1.31
 3     3        -0.444          -0.132         0.312               1.37
 4     4        -0.439          -0.0982        0.340               1.41
 5     5        -0.383          -0.266         0.117               1.12
 6     6        -0.541          -0.0903        0.450               1.57
 7     7        -0.512          -0.111         0.401               1.49
 8     8        -0.493          -0.152         0.341               1.41
 9     9        -0.527          -0.175         0.352               1.42
10    10        -0.491          -0.257         0.234               1.26
# i 3,990 more rows
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{nas\_prop\_bm\_diff }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{reframe}\NormalTok{(}
    \CommentTok{\# 90\% CrI}
    \AttributeTok{q90 =} \FunctionTok{quantile2}\NormalTok{(voicing\_diff\_ratio, }\AttributeTok{probs =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.05}\NormalTok{, }\FloatTok{0.95}\NormalTok{)),}
    \CommentTok{\# 80\% CrI}
    \AttributeTok{q80 =} \FunctionTok{quantile2}\NormalTok{(voicing\_diff\_ratio, }\AttributeTok{probs =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.1}\NormalTok{, }\FloatTok{0.9}\NormalTok{)),}
    \CommentTok{\# 60\% CrI}
    \AttributeTok{q60 =} \FunctionTok{quantile2}\NormalTok{(voicing\_diff\_ratio, }\AttributeTok{probs =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.2}\NormalTok{, }\FloatTok{0.8}\NormalTok{)),}
\NormalTok{  ) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\FunctionTok{across}\NormalTok{(}\FunctionTok{everything}\NormalTok{(), }\SpecialCharTok{\textasciitilde{}}\FunctionTok{round}\NormalTok{(.x, }\DecValTok{2}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

@@

Moving onto question 2: is there individual speaker variation?
{[}TAMMINGA XXX{]} For this, we will use the \texttt{spread\_draws()}
function from tidybayes {[}XXX{]} to extract the draws of the varying
terms (in brms these are the coefficients that start with \texttt{r\_}).
There is quite a few steps of processing to get from the raw draws to
the estimand we need: while we have commented the following code, we
encourage readers to test each line sequentialy and inspect the
intermediate output to fully understand the process. We assume that
readers are familiar enough with models with varying terms (aka random
effects, mixed-effects models). What readers should note is that to
obtain the expected predictions of nasalisation proportion for each
speaker, the constant terms and the varying terms should be added (since
the varying terms indicate the deviation of each speaker from the
overall estimate).

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(tidybayes)}

\NormalTok{nas\_prop\_r }\OtherTok{\textless{}{-}}\NormalTok{ nas\_prop\_bm }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# extract draws from model, only \textasciigrave{}r\_speaker\textasciigrave{} varying terms}
  \FunctionTok{spread\_draws}\NormalTok{(r\_speaker[speaker,voicingvowel]) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# separate the column voicingvowel to two columns}
  \FunctionTok{separate}\NormalTok{(voicingvowel, }\FunctionTok{c}\NormalTok{(}\StringTok{"voicing"}\NormalTok{, }\StringTok{"vowel"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# join the draws with the \textasciigrave{}b\_\textasciigrave{} terms}
  \FunctionTok{left\_join}\NormalTok{(}\AttributeTok{y =}\NormalTok{ nas\_prop\_bm\_draws\_long) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# get the expected log{-}odd value of each speaker, in each draw}
  \CommentTok{\# this is the sum of the \textasciigrave{}value\textasciigrave{} from the b\_ terms and the value from the}
  \CommentTok{\# r\_speaker term.}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{r\_speaker\_value =}\NormalTok{ value }\SpecialCharTok{+}\NormalTok{ r\_speaker) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# group the data for summarise}
  \FunctionTok{group\_by}\NormalTok{(.draw, speaker, voicing) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# get mean expected log{-}odds by draw, speaker and voicing (averaging across vowel)}
  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{r\_speaker\_value\_mean =} \FunctionTok{mean}\NormalTok{(r\_speaker\_value)) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# make the data wider: two columns, one for voiced and one for voiceless}
  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ voicing, }\AttributeTok{values\_from =}\NormalTok{ r\_speaker\_value\_mean) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# finally, calculate the difference in expected log{-}odds of voiceless and voiced}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{voicing\_diff =}\NormalTok{ voicingvoiceless }\SpecialCharTok{{-}}\NormalTok{ voicingvoiced)}

\NormalTok{nas\_prop\_r}
\end{Highlighting}
\end{Shaded}
